A Transformer-based Pretrained Language Model for Chinese Law Examination

### 2021-01-05 A-BasicCommom/ACL2021/acl_law_examination.tex
1. add law examination model.

\title{A Transformer-based Pretrained Language Model for Automatic Document Summarization}

@@

\begin{document}
\maketitle
\begin{abstract}
 Document summarization is an essential task in the information retrieval.
 User intention for specific documents is hard to satisfy for the information overload,
 thus there are rarely golden standards for matching a certain document.
 I propose a multi-grained summarization model for documents that uses attention on paragraphs,
 supervised learning on the sentence importance, and sequence-to-sequence learning on characters and words.
 Tested on the 2020 Chinese Law Summarization Dataset, the proposed model achieved
 better performance than other modern summarization models.
\end{abstract}

@@

Document matching is an essential task in daily work and study.
Because the matching algorithm is not capable of choosing important words from the massive documents,
to use the content of a document as the matching criteria often fails in returning unintended documents.
Document summarization condenses long documents into short paragraphs by retaining core information.
Thus, a much wiser way for the document matching is using the summarization instead of the content.

@@

\citet{bhargava2020deep} use Convolutional neural network and Long-Short Term Memory network in the paraphrase detection of
documents and summaries, then using multi-grained Convolutional neural networks as the sentence extraction model,
as a result, the F1 scores on the English and Malayalam summarization corpus are 31.57\% and 53.57\%.

\citet{erera2019summarization} consider the summarization problem as a query problem, use query
saliency, entities coverage, diversity, text coverage and sentence length as the objectives.

\citet{altmami2020automatic} concluded the special pattern for the summarization of scientific articles,
and found that abstract generation-based and citation-based are two notice-worth solutions.

\citet{polsley2016casesummarizer} used a combined word frequency and domain knowledge summary method for the legal text abstraction,
and achieved an average of 10.9\% ROUGE score between automatically-generated summaries, and the expert-generated summaries.

\citet{iqbal2020survey} showed that the deep learning approaches have achieved many satisfactory results in several domains,
Word embeddings, such as Word2Vec, Glove, and FastText are widely used in the Natural Language Processing.
Variational Auto-Encoders and Generative Adversarial Networks have been used for the text generations.

\citet{litvak2019easy} studied the evaluation system for text summarization,
and showed that ROUGE, MeMoG for quality evaluation, Latent Dirichlet allocation for topic evaluation,
and grammar analysis for the readability evaluation.

\citet{deng2020two} used a Sequence-to-Sequence generation model and an adversarial model in the text summarization for Chinese texts.

\citet{zhang2019pretraining} used the Transformer network in encoder-decoder framework for the text summarization task, and
achieved a Rouge score of 33.48\% in the CNN/DailyMail dataset for news summarization.

\citet{xiao2019extractive} used the extractive LSTM-Minus model in the text summarization task, and by combining
global document level, sentence level and topic segment representation in the network, achieved a Rouge score of 31.99\%
in the Pubmed summarization dataset.

\citet{liakata2013discourse} used the CRF and SVM models for the sentence extractive summarization for the scientific articles.
\citet{cohan2015scientific} use the important sections in scientific papers as criteria for selecting important sentence.

\citet{sutskever2013importance} started to use sequence-to-sequence neural networks in abstractive summarization.
\citet{vinyals2015pointer} introduced copy mechanism from source to summary in sequence-to-sequence models.

\begin{figure*}
\begin{center}
  \fbox{\rule{0pt}{2in} \includegraphics[width=0.9\linewidth]{SummaryRule.pdf}}
\end{center}
   \caption{Rule based segment and importance based summarization.}
\label{fig:short}
\end{figure*}

\section{Hierachical Multi-grained Summarization}
\label{sec:hireachy}

Documents have their own organizations by different purposes, take the civil legal documents as an example,
There are 123 different kinds of arguing reasons in the Chinese Court Sentence Documents.
Largely list as follows:
\begin{itemize}
\item Disputes over personality rights,
\item Marriage, family, inheritance disputes,
\item Property rights disputes,
\item Contract, management without cause, disputes over unjust enrichment,
\item Labor disputes, personnel disputes,
\item Maritime disputes,
\item Civil disputes related to companies, securities, insurance, bills, etc.
\item Inciting disputes
\end{itemize}
However, each of these documents follow the same organization of segments, for example,
the purpose, the facts, the court opinions and the trail results.
Thus, for a meaningful text summarization includes all there segments of importance and ignore other segments.

@@

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{Accuracy} \\
\hline
RoBERTa & 768 & 12 & 42.05\% \\
RBT3 & 768 & 3 & 40.18\% \\
RBT3L & 1024 & 3 & 41.22\% \\
\hline
\end{tabular}
\caption{Different Pre-trained Language models accuracy in the sequence to sequece training steps.}
\end{table}

@@

\bibliographystyle{acl_natbib}
\bibliography{anthology,acl2021,acl_summary}

>>>>

\title{A Transformer-based Pretrained Language Model for Chinese Law Examination}

@@

\begin{document}
\maketitle
\begin{abstract}
 Teaching machines to take examinations of the National Judicial Examination of China is a meaningful task.
 However, until now perfect solution for the Question Answering is still missing.
 In this paper, I demonstrate a novel model which leverage the Transformers and Convolutional Neural Networks for the Judicial Examination task,
    propose model achieved 35\% in accuracy.
\end{abstract}

@@

  Legal Question Answering aims to provide explanations, advice and solutions for legal issues.
Reading Comprehension and Open-domain Question Answering are two of the most studied topics in the natural processing language.

@@

\citet{hermann2015teaching} found that the combination of the Deep LSTM encoders, and the Attention model works better on the Daily Mail reading comprehension dataset,
 and by document representation with the token-level question representation the Attention model achieved better result on the CNN reading comprehension dataset.

\citet{hashemi2019performance} proposed an efficient evaluation method for the question answering, compared to the extensive study in
the retrieval tasks, the proposed neural model for evaluating query performance prediction showed that its outstanding in all the methods in the QA domain.

\citet{huang2019knowledge} borrowed idea from the knowledge graph completion and recommender system, they use the low-dimensional vector learned from knowledge graph,
then trained the question answering model.

\citet{karki2019question} broke the question answering problem into several subtasks, such as table retrieval and element classification.
the performace of the translation from a question to SQL clause is still far from satisfactory, with 15.6\% to 19.5\% in the F1 score on the test dataset.

\citet{mcelvain2019non} showed that for the non-factoid question answering task in the legal domain, legally correct, jurisdictional relevant, and conversationally responsive answers
are three key factors.

\citet{jin2019video} described that by understanding the question and the contextual images, the Attention model learn the answers, the total accuracy achieved 30.2\% in the YouTube-QA Dataset.

\citet{pizzato2008indexing} proposed the weight based bag-of-words, partial relation and full relation to model semantic roles for questions as labels in the training procedure.

\citet{zhan2020medical} proposed an Attention-based reasoning model in the medical visual question answering.

\citet{qu2020open} studied a transformer-based conversational QA system, and use retrieval and rerank pattern to solve the problem.

\section{Methodology}
\label{sec:hireachy}

@@

\begin{table}
\centering
\begin{tabular}{cccc}
\hline
\textbf{Model} & \textbf{Neurons}& \textbf{Layers} & \textbf{Accuracy} \\
\hline
RoBERTa & 768 & 12 & 42.05\% \\
RBT3 & 768 & 3 & 40.18\% \\
RBT3L & 1024 & 3 & 41.22\% \\
\hline
\end{tabular}
\caption{Pre-trained language models accuracy in the sequence-to-sequece training steps.}
\end{table}

@@

\bibliographystyle{acl_natbib}
\bibliography{anthology,acl2021,acl_examination}
